---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# equationer

[![Build Status](https://travis-ci.com/UBESP-DCTV/equationer.svg?token=LB47B8iKQhmYmrAuxwVQ&branch=master)](https://travis-ci.com/UBESP-DCTV/equationer)
[![Coverage status](https://codecov.io/gh/UBESP-DCTV/equationer/branch/master/graph/badge.svg)](https://codecov.io/github/UBESP-DCTV/equationer?branch=master)

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![CRAN status](https://www.r-pkg.org/badges/version/equationer)](https://cran.r-project.org/package=equationer)

The goal of the package `equationer` is to implement an environment to
consistently generate the estimations from the equations reported in the
paper "Review of Equations of Energy Requirements" by the
*Unit of Biostatistics, Epidemiology and Public Health* of the University
of Padova.


## Installation

You can install the development version of `equationer` from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/equationer")
```


## Code of Conduct

Please note that the `equationer` project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By
contributing to this project, you agree to abide by its terms.
